### 2019-08-13 tess.tex
More writting in TESS and TRAMOS chapter

@@

>>>>

In the following subsections, I present a re-analisys of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively. TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be download directly.

In order to compute the transit time of each light curve, I used EXOFASTv2 but only to fit the transit time. The remaining planetary parameters were fixed with the values from Tables \ref{tab:wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.

@@

The star WASP-18 was observed continuously during Sector 2 and 3 of the TESS mission, between August 22nd and October 18th, 2018. Theses observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and then included into the TTV analysis. Figure \ref{wasp18_ttv} shows the

### 2019-08-13 tramos.tex
More writting in TESS and TRAMOS chapter

Since the discovery of \cite{Holman2010}, around 20 exoplanets have been discovered and characterized thanks to the measurement of variations on their transit times and the following proper dynamical modelling of the system. Most of them are Kepler systems because of its high duty-cycle, on which it provided years on transits data. Kepler stopped working on 2018, but the Transit Exoplanet Satellite Survey (TESS) is currently providing its first results providing planetary systems showing TTVs.  For example, two exoplanets (possibly one Jupiter and a sub-Saturn like) were recently discovered by \cite{Dawson2019} orbiting TOI-216, in near 2:1 resonance.

>>>>

Since the discovery of \cite{Holman2010}, around 20 exoplanets have been discovered and characterized thanks to the measurement of variations on their transit times and the following proper dynamical model ling of the system. Most of them are Kepler systems because of its high duty-cycle, on which it provided years on transits data. Kepler stopped working on 2018, but the Transit Exoplanet Satellite Survey (TESS) is currently providing its first results providing planetary systems showing TTVs.  For example, two exoplanets (possibly one Jupiter and a sub-Saturn like) were recently discovered by \cite{Dawson2019} orbiting TOI-216, in near 2:1 resonance.

To date, only two hot Jupiters have been found to show TTV signals due to the presence of additional companions on their systems: WASP-47b \citep{Becker2015} and Kepler-730b \citep{Canas2019}, even though the TTV was proposed as a technique to search for additional companions of gas giants. The lack of observed companions in hot Jupiter systems could provide crucial information about planetary formation processes.

Trough the TTV method not only the transiting exoplanet is being studied but the whole planetary system. Even the lack of variation in the transit timing gives clues related to the formation of close-in gas giant.
